
Kaggle Digit Recognizer

knn_benchmark.R baseline solution
---------------------------------

This is the knn_benchmark.R solution directly from Kaggle except as noted below
* Requires package FNN 
* Project setup assumed to be like this:
 * [localprojectroot]
 * [localprojectroot]/digit
 * [localprojectroot]/digit/src _# rmd, md, html and csv-output files_
 * [localprojectroot]/digit/data _# csv-input files from Kaggle (train.csv and test.csv)_

Added: timing code
```{r}
startClock <- proc.time()
```
This section is directly from the Kaggle knn_benchmark.R solution:
```{r}
library(FNN)

train <- read.csv("../data/train.csv", header=TRUE)
test <- read.csv("../data/test.csv", header=TRUE)

# To test subset:
# train <- train[1:100,]
# test <- test[1:100,]

labels <- train[,1]
train <- train[,-1]
results <- (0:9)[knn(train, test, labels, k = 10, algorithm="cover_tree")]
```
The Kaggle knn_benchmark.R example writes a single column of predicted digits to the output file, but that format isn't accepted by Kaggle when you submit it.  Instead, two columns are needed as follows: the first column is simply the row number and the second column is the predicited digit. The two columns are separated by a comma.
```{r}
# Invalid format:
#write(results, file="knn_benchmark.csv", ncolumns=1)
# Correct format:
write(t(cbind(c(1:length(results)), results)), file="knn_benchmark.csv", ncolumns=2, sep=",")
```
Added: timing code
```{r}
cat("elapsed minutes: ", (proc.time()[3] - startClock[3])/60)
```
